\section{Structural Audit: Constrained Mixing Analysis}

The standard approach to flavor physics fits the CKM and PMNS matrices to data parameters. We invite the neutrino and flavor physics communities (e.g., T2K, NOvA, DUNE, Belle II) to invert this process, using the lattice invariants as fixed priors.

\subsection{Neutrino Global Fit (Geometric Prior)}

\textbf{Task:} Run the global neutrino oscillation fit (NuFIT) with the mixing angles locked to the exact geometric ratios derived from the lattice projection:
\begin{itemize}
    \item \textbf{Solar Angle:} $\sin^2 \theta_{12} = \frac{1}{2\phi} \approx \SolarAngleVal$ (The Golden Ratio Aperture).
    \item \textbf{Atmospheric Angle:} $\sin^2 \theta_{23} = \frac{1}{\chi} = 0.5$ (Maximal Mixing).
    \item \textbf{Reactor Angle:} $\sin^2 \theta_{13} = \frac{3}{\alpha^{-1}} \approx \ReactorAngleVal$ (The Interaction Leak).
\end{itemize}

\textbf{Expected Result:} The ``Geometric Prior" fits the global data within $1\sigma$, naturally resolving the octant degeneracy in $\theta_{23}$ by enforcing maximal mixing.

\textbf{Falsification Criterion:} A global fit degradation of $\Delta\chi^2 > 9$ ($3\sigma$) compared to the standard floating-parameter fit.

\subsection{Rare Decay Precision Test (\texorpdfstring{$K \to \pi\nu\bar{\nu}$}{Ktopinubar})}

\textbf{Task:} Compare NA62 and KOTO event rates directly to geometrically derived scattering cross-sections based on the vacuum impedance ($\alpha^2$) and the CKM geometric interference ($V_{ts}$).

\textbf{Expected Result:} Event rates align with geometric impedance predictions without requiring effective field theory loop corrections.


\CatchFileBetweenTags{\flavorTotalChiVal}{calculations/flavor_geometry.tex}{flavorTotalChiVal}
\CatchFileBetweenTags{\flavorReducedChiVal}{calculations/flavor_geometry.tex}{flavorReducedChiVal}

\subsection{The Zero-DOF Global Fit}

As a proof of principle, we performed a global consistency check of 11 flavor observables (CKM elements, Jarlskog invariant, Triangle angles, and PMNS angles) with zero free parameters.

\begin{equation}
    \chi^2_{total} \approx \flavorTotalChiVal \quad (\text{Reduced } \chi^2 \approx \flavorReducedChiVal)
\end{equation}

The fact that $\chi^2_{red} < 1$ indicates that the geometric constraints ($D, \sigma, \chi$) naturally encode the correlations present in the experimental data, rendering the 18 arbitrary parameters of the Standard Model flavor sector redundant.