\section{Conclusion: The Geometry of Transition}

We have shown that the flavor sector of the Standard Model is not a domain of random mixing angles, but a structured protocol of \textbf{Boundary State Transitions}. The disparity between the diagonal CKM matrix (Quarks) and the anarchic PMNS matrix (Neutrinos) is resolved by the structural duality between \textbf{Topological Solitons} (constrained by interface drag) and \textbf{Lattice Phonons} (coupling to global symmetry).

Crucially, we have derived the \textbf{Gatto-Sartori-Tonin (GST) Relation} from first principles, demonstrating that the Weak Mixing Angle ($\sin^2 \theta_W$) and the Cabibbo Angle ($\sin \theta_C$) are structurally coupled partitions of the single systemic capacity ($N_{sys}$). This unifies the Gauge and Flavor sectors under a single resource constraint. Furthermore, we demonstrated that the suppression of third-generation mixing ($V_{td}, V_{ts}$) is not a free parameter, but the result of \textbf{Destructive Geometric Interference} driven by the vacuum's twist.

While traditional Grand Unified Theories attempt to merge gauge groups at high energies, this framework suggests a different path to unification: Structural Unity. By deriving both the Weak Mixing Angle (Force) and the Cabibbo Angle (Flavor) from the same finite channel capacity, we demonstrate that the distinct sectors of the Standard Model are not separate modules, but interleaved data streams on a single hardware substrate.

Finally, the precise derivation of the Jarlskog Invariant ($J \approx \JarlskogMatrixVal$) identifies \textbf{CP Violation} as the inescapable topological phase offset of the Chiral Diode ($\delta \approx \CPPhaseVal$), establishing the arrow of time not as a thermodynamic accident, but as a geometric necessity of the substrate.

\subsection{Scope: Boundary Conditions vs. Dynamics}
This work derives the fundamental constants as the static \textbf{Boundary Conditions} of the vacuum geometry. It does not attempt to derive the dynamic equations of motion (e.g., scattering amplitudes or loop corrections). In this framework, standard Quantum Field Theory is the effective dynamic description of information flowing \textit{through} these fixed geometric apertures. The ``running" of constants (Renormalization) is interpreted here as the scale-dependent resolution of the lattice granularity, a topic reserved for future work.

\subsection{Audits}
To ensure the structural integrity of this framework, we provide two rigorous audits of the underlying geometry. In Appendix \ref{sec:GeometricAudits}, we demonstrate that the interaction invariants ($\sigma, \chi$) necessitate the QCD Axial Anomaly ($N_c=3$) and the Weinberg Angle unification ($3/8$) without fine-tuning. Furthermore, because this work relies on static geometric boundaries to define dynamic transitions, we derive the explicit mechanism of time evolution in Appendix \ref{sec:EmergentDynamics}. We show that the standard Dirac Operator emerges naturally from a discrete cellular automaton rule (The Kirchhoff Update) acting on the chiral lattice nodes.