\CatchFileBetweenTags{\AlphaInvVal}{calculations/constants.tex}{AlphaInvVal}

\textit{Informational Energetics: Nested Persistence} established that the vacuum partitions its finite channel capacity ($\nu=16$) across orthogonal geometric sectors. But partitioning is only half the problem. For the partitioned system to function as a coherent whole, information must flow across the boundaries between sectors. This paper derives the universal geometry of that flow.


\section{Introduction}
The Standard Model provides a phenomenologically flawless description of the flavor sector, parameterizing quark and lepton mixing through the CKM and PMNS matrices. However, while the mathematical framework of these unitary matrices precisely tracks observed transition rates, their specific values are inserted as experimentally measured inputs and leaves the flavor sector dependent on over 18 free parameters.

This kinematic success leaves open the geometric question: why do these specific parameter values, rather than others, minimize Entropic Action on the vacuum substrate? The mixing angles of quarks are small and hierarchically suppressed, while the mixing angles of neutrinos are large and near-maximal. Standard field theory accommodates this dramatic disparity perfectly, but it offers no foundational mechanism to explain \textit{why} the two sectors behave so differently under the same unitary mathematics.

In the \textit{$E_8$-Persistence Theory}, we approach this not by altering the Standard Model, but by providing its geometric initialization. We define Flavor as the Geometric Address of a resonance tier, the discrete lattice coordinates that specify a particle's internal symmetry state, playing the same role as the abstract quantum numbers of the Standard Model, but emerging from substrate topology rather than postulated symmetry. Consequently, flavor mixing is identified as a \textbf{Boundary State Transition} at the interface of these lattice tiers.

\subsection{Foundational Priors}
This paper applies the partitioning rules to the $E_8$ substrate established in \cite{meyer_informational_2026, meyer_ieaction_2026}, characterized by the invariant integer set $\mathbb{S}=\{\Delta=43\text{ (temporal)}, \nu=16\text{ (chiral)}, \sigma=5\text{ (interaction)}, \chi=2\text{ (topological)}\}$ and the geometric impedance $\alpha^{-1}\approx \AlphaInvVal$. All derivations herein treat these as rigid priors; zero additional free parameters are introduced.

Here we evaluate these transitions as thermodynamic pathways minimizing Entropic Action.

\begin{enumerate}
    \item \textbf{The Geometric Determination of Flavor Matrices:} The Geometric Determination of Flavor Matrices: The CKM and PMNS parameters emerge as closed-form geometric aspect ratios, with mixing hierarchies fixed by lattice topology rather than empirical input.
    
    \item \textbf{The Structural Coupling of Gauge and Flavor Sectors:} The Gatto-Sartori-Tonin relation emerges as an impedance-matching condition between the Weak Mixing Angle and the Cabibbo Angle, both partitioning the same finite channel capacity.
\end{enumerate}

\textbf{Scope and Continuity:} All fundamental inputs utilized in these derivations; including the discrete lattice capacity ($\nu=16$), interaction rank ($\sigma=5$), topological boundary ($\chi=2$), spatial manifold ($D=4$), and the vacuum impedance ($\alpha^{-1} \approx \AlphaInvVal$) are taken strictly as rigid priors established in ``Informational Energetics: A Universal Architecture of Persistence''\cite{meyer_informational_2026}, ``Informational Energetics: Entropic Action''\cite{meyer_ieaction_2026}, ``Informational Energetics: Nested Persistence''\cite{meyer_ienested_2026}. \textit{Zero free parameters} are introduced to fit the flavor data.