\section{The Logic of Transition: Impedance Power Transfer}

Before deriving the specific mixing angles that govern flavor transitions, we must establish the general mechanism of state transition on the $E_8$ lattice. Unlike standard field theory, which treats interactions as point-like couplings, Informational Energetics models them as \textbf{Impedance Power Transfer} events subject to Kirchhoff's laws of information flow.

\subsection{The Admittance Amplitude (\texorpdfstring{$\sqrt{\alpha}$}{sqrtalpha})}
A topological defect (particle) maintains stability against the vacuum impedance $Z_{vac} = \alpha^{-1}$ (derived in Paper I). 

An interaction acts as a ``Topological Splice'' that relaxes geometric stress by shedding a coordination signal. 

An interaction represents a \textbf{Topological Splice}—a geometric operation that conserves information density while allowing the knot to shed accumulated stress via a coordination signal (boson). The probability amplitude $\mathcal{A}$ of this event is defined by the Admittance of the lattice node:
\begin{equation}
\mathcal{A} \propto \frac{1}{\sqrt{Z_{vac}}} = \sqrt{\alpha}
\end{equation}
This recovers the standard QED vertex factor ($e = \sqrt{4\pi\alpha}$), identifying electric charge as the geometric admittance of the substrate.

\subsection{Dynamic Validation: Scattering Cross-Section}
To verify that this impedance logic holds dynamically, we derive the scattering cross-section for electron-positron annihilation ($e^+e^- \to \mu^+\mu^-$). In the lattice, this represents power transfer across the Bulk Interaction Geometry.

\begin{enumerate}
    \item \textbf{Coupling Efficiency ($\eta_C$):} The total probability scales with the square of the input and output admittances: $\eta_C = (\sqrt{\alpha} \cdot \sqrt{\alpha})^2 = \alpha^2$.
    \item \textbf{Geometric Factor (1/3):} The signal propagates through the \textbf{Interaction Remainder} ($\sigma - \chi = 3$), representing the three spatial dimensions of the manifold bulk. Vector projection onto this 3D geometry introduces a normalization factor of $1/(\sigma - \chi) = 1/3$.
    \item \textbf{Aperture ($1/s$):} Unitarity requires the interaction area to scale with the inverse square of the center-of-mass energy ($1/s$).
\end{enumerate}

Combining these factors with the circular interface ($4\pi$):
\begin{equation}
\sigma_{E8} = \frac{4\pi \alpha^2}{3s}
\end{equation}
This exact recovery of the high-energy QED limit confirms that interaction probabilities are governed by geometric impedance matching. We now apply this same logic to the \textbf{Internal Transitions} (Flavor Mixing) between lattice resonance tiers.

\subsection{Geometric Validation: The Schwinger Limit (Complexity vs. Topology)}

Before applying this framework to the complexities of flavor mixing, we demonstrate the predictive power of the geometric approach by recovering a foundational result of Quantum Electrodynamics (QED): the anomalous magnetic moment of the electron ($a_e$).

In standard QFT, this value arises from virtual particle loops in the vacuum state. The first-order correction, calculated by Julian Schwinger in 1948, is exactly:
\begin{equation}
a_e = \frac{\alpha}{2\pi} \approx 0.0011614
\end{equation}

Deriving this value in QFT requires evaluating the one-loop vertex correction diagram, a complex process involving renormalization, infrared regularization, and integration over Feynman parameters. In $E_8$-Persistence, this is not a calculus problem; it is a \textbf{Geometric Aspect Ratio}.

\subsubsection{The Geometric Setup}

The electron is a geometric knot with Unitary Address ($N=0$) coupled to the Gauge Connection (the photon). The interaction is defined by two invariant properties:

\begin{itemize}
    \item \textbf{The Flux ($\alpha$):} The strength of the interaction is governed by the Vacuum Admittance coefficient $\alpha$ (derived in Paper I).
    \item \textbf{The Topology ($2\pi$):} While the electron spinor lives on the ``double cover" of the manifold ($4\pi$), the vector gauge field (photon) propagates along the manifold boundary, which has a fundamental cycle of $2\pi$.
\end{itemize}

\subsubsection{The Derivation}

The anomalous moment represents the \textbf{Geometric Phase Lag} between the linear gauge field and the topological knot. It is simply the ratio of the Coupling Flux to the Gauge Cycle:

\begin{equation}
a_e = \frac{\text{Coupling Flux}}{\text{Gauge Cycle}} = \frac{\alpha}{2\pi}
\end{equation}

\subsubsection{Conclusion: The Power of Geometry}

The validity of the geometric approach is highlighted by contrasting the computational cost required to reach the identical result:

\begin{itemize}
    \item \textbf{Standard QED (Perturbative):} Derives $a_e$ via Feynman Loop Integrals. \\ \textit{Complexity:} High (Renormalization required).
    \item \textbf{$E_8$-Persistence (Geometric):} Derives $a_e$ via the Aspect Ratio of the flux-topology coupling. \\ \textit{Complexity:} Zero (Algebraic identity).
\end{itemize}

The famous ``Alpha over Two Pi" is not the result of a complex integral; it is the fundamental aspect ratio of a linear flux ($\alpha$) wrapping a circular manifold ($2\pi$). We now apply this same topological simplicity to the disparate mixing angles of the flavor sector.