\section{The CKM Unitary Matrix Representation: Full Generational Consistency}

In standard particle physics, the unitarity of the CKM matrix is a fundamental postulate. In the $E_8$-Persistence Theory, this conservation is a physical consequence of State Saturation.

Because the total causal flow is restricted to the 16 chiral channels of the $E_8$ substrate, the information density cannot exceed unity. Probability conservation is enforced by the State Space Limit. Consequently, the sum of Persistence probability (authorized tier stability) and Leakage probability (interface shifts) must equate to exactly $1.0$ for each generational row and column. This Unitary Solvency ensures that the ``Standard Model" software remains synchronized with the available chiral density.

\subsection{The Full CKM Derivation Table (Magnitudes)}

Table \ref{tab:ckm_derivation} presents the complete geometric derivation of the CKM matrix elements. These values are calculated directly from the lattice invariants without reference to experimental data or fitted parameters.

\subsubsection*{Note on Geometric Precision: Topology vs. Volume}

A critical feature of this derivation is the absence of the Manifold Quantization Efficiency ($\eta \approx 0.994$) that appeared in the mass derivations of Paper I. In the $E_8$-Persistence framework, physical observables fall into two distinct geometric classes:

\begin{itemize}
    \item \textbf{Volumetric Quantities (Mass, Charge, Coupling):} These represent the \emph{content} of the lattice nodes. Because they fill the bulk manifold, they are subject to the projection overhead ($\eta$) of mapping discrete lattice bits into continuous spacetime volume.
    
    \item \textbf{Topological Quantities (Mixing Angles, Phases):} These represent the \emph{boundaries} between states. A boundary on an integer lattice is a precise topological cut. The geometry of an interface (e.g., the aspect ratio $\pi/14$) is determined strictly by the integer coordinates of the boundary nodes, independent of the node capacity.
\end{itemize}

Consequently, Flavor Mixing angles are derived as \textbf{Exact Geometric Ratios}, providing a rigid test of the lattice topology unblurred by thermodynamic friction.

% --- Load Dynamic Constants from Python Output ---
% Gen 1
\CatchFileBetweenTags{\VudVal}{calculations/flavor_geometry.tex}{VudVal}
\CatchFileBetweenTags{\VudEq}{calculations/flavor_geometry.tex}{VudEq}
\CatchFileBetweenTags{\VudExp}{calculations/flavor_geometry.tex}{VudExperimentalValue}
\CatchFileBetweenTags{\VudSig}{calculations/flavor_geometry.tex}{VudSigma}

\CatchFileBetweenTags{\CabibboSineVal}{calculations/flavor_geometry.tex}{CabibboSineVal}
\CatchFileBetweenTags{\CabibboSineEq}{calculations/flavor_geometry.tex}{CabibboSineEq}
\CatchFileBetweenTags{\CabibboSineExp}{calculations/flavor_geometry.tex}{CabibboSineExperimentalValue}
\CatchFileBetweenTags{\CabibboSineSig}{calculations/flavor_geometry.tex}{CabibboSineSigma}

\CatchFileBetweenTags{\VubVal}{calculations/flavor_geometry.tex}{VubVal}
\CatchFileBetweenTags{\VubEq}{calculations/flavor_geometry.tex}{VubEq}
\CatchFileBetweenTags{\VubExp}{calculations/flavor_geometry.tex}{VubExperimentalValue}
\CatchFileBetweenTags{\VubSig}{calculations/flavor_geometry.tex}{VubSigma}

% Gen 2
\CatchFileBetweenTags{\VcdVal}{calculations/flavor_geometry.tex}{VcdVal}
\CatchFileBetweenTags{\VcdEq}{calculations/flavor_geometry.tex}{VcdEq}
\CatchFileBetweenTags{\VcdExp}{calculations/flavor_geometry.tex}{VcdExperimentalValue}
\CatchFileBetweenTags{\VcdSig}{calculations/flavor_geometry.tex}{VcdSigma}

\CatchFileBetweenTags{\VcsVal}{calculations/flavor_geometry.tex}{VcsVal}
\CatchFileBetweenTags{\VcsEq}{calculations/flavor_geometry.tex}{VcsEq}
\CatchFileBetweenTags{\VcsExp}{calculations/flavor_geometry.tex}{VcsExperimentalValue}
\CatchFileBetweenTags{\VcsSig}{calculations/flavor_geometry.tex}{VcsSigma}

\CatchFileBetweenTags{\VcbVal}{calculations/flavor_geometry.tex}{VcbVal}
\CatchFileBetweenTags{\VcbEq}{calculations/flavor_geometry.tex}{VcbEq}
\CatchFileBetweenTags{\VcbExp}{calculations/flavor_geometry.tex}{VcbExperimentalValue}
\CatchFileBetweenTags{\VcbSig}{calculations/flavor_geometry.tex}{VcbSigma}

% Gen 3
\CatchFileBetweenTags{\VtdVal}{calculations/flavor_geometry.tex}{VtdVal}
\CatchFileBetweenTags{\VtdEq}{calculations/flavor_geometry.tex}{VtdEq}
\CatchFileBetweenTags{\VtdExp}{calculations/flavor_geometry.tex}{VtdExperimentalValue}
\CatchFileBetweenTags{\VtdSig}{calculations/flavor_geometry.tex}{VtdSigma}

\CatchFileBetweenTags{\VtsVal}{calculations/flavor_geometry.tex}{VtsVal}
\CatchFileBetweenTags{\VtsEq}{calculations/flavor_geometry.tex}{VtsEq}
\CatchFileBetweenTags{\VtsExp}{calculations/flavor_geometry.tex}{VtsExperimentalValue}
\CatchFileBetweenTags{\VtsSig}{calculations/flavor_geometry.tex}{VtsSigma}

\CatchFileBetweenTags{\VtbVal}{calculations/flavor_geometry.tex}{VtbVal}
\CatchFileBetweenTags{\VtbEq}{calculations/flavor_geometry.tex}{VtbEq}
\CatchFileBetweenTags{\VtbExp}{calculations/flavor_geometry.tex}{VtbExperimentalValue}
\CatchFileBetweenTags{\VtbSig}{calculations/flavor_geometry.tex}{VtbSigma}

\begin{table*}[h]
\centering
\caption{\textbf{Derivation of CKM Matrix Elements.} Comparison of geometric predictions (System III) against PDG 2024 global fit values. Note that $V_{td}$ and $V_{ts}$ are derived via destructive interference involving the CP phase $\delta \approx 68^\circ$, explaining their suppression without arbitrary parameters.}
\label{tab:ckm_derivation}
\renewcommand{\arraystretch}{1.8} 
\setlength{\tabcolsep}{5pt}
\begin{tabular}{@{} l l l c c r @{}} 
\toprule
\textbf{Transition} & \textbf{Elem.} & \textbf{Geometric Logic / Formula} & \textbf{Predicted} & \textbf{Target (PDG)} & \textbf{Dev.} \\
\midrule
\multicolumn{6}{l}{\textit{Generation 1 (Chiral Aperture)}} \\
$u \to d$ & $V_{ud}$ & Unitary Persistence ($\VudEq$) & \textbf{\VudVal} & \VudExp & $\VudSig\sigma$ \\
$u \to s$ & $V_{us}$ & Cabibbo Aperture ($\CabibboSineEq$) & \textbf{\CabibboSineVal} & \CabibboSineExp & $-\CabibboSineSig\sigma$ \\
$u \to b$ & $V_{ub}$ & Quantum Tunneling ($\VubEq$) & \textbf{\VubVal} & \VubExp & $-\VubSig\sigma$ \\
\midrule
\multicolumn{6}{l}{\textit{Generation 2 (Dimensional Shift)}} \\
$c \to d$ & $V_{cd}$ & Unitary Reflection ($\VcdEq$) & \textbf{\VcdVal} & \VcdExp & $-\VcdSig\sigma$ \\
$c \to s$ & $V_{cs}$ & Unitary Persistence ($\VcsEq$) & \textbf{\VcsVal} & \VcsExp & $+\VcsSig\sigma$ \\
$c \to b$ & $V_{cb}$ & Manifold Drag ($\VcbEq$) & \textbf{\VcbVal} & \VcbExp & $+\VcbSig\sigma$ \\
\midrule
\multicolumn{6}{l}{\textit{Generation 3 (Interference \& Closure)}} \\
$t \to d$ & $V_{td}$ & Phase Interference ($\VtdEq$) & \textbf{\VtdVal} & \VtdExp & $+\VtdSig\sigma$ \\
$t \to s$ & $V_{ts}$ & Phase Interference ($\VtsEq$) & \textbf{\VtsVal} & \VtsExp & $+\VtsSig\sigma$ \\
$t \to b$ & $V_{tb}$ & Unitary Persistence ($\VtbEq$) & \textbf{\VtbVal} & \VtbExp & $-\VtbSig\sigma$ \\
\bottomrule
\end{tabular}
\end{table*}



% --- Load Full Matrix Tags ---
\CatchFileBetweenTags{\VcdVal}{calculations/flavor_geometry.tex}{VcdVal}
\CatchFileBetweenTags{\VtdVal}{calculations/flavor_geometry.tex}{VtdVal}
\CatchFileBetweenTags{\VtsVal}{calculations/flavor_geometry.tex}{VtsVal}
\CatchFileBetweenTags{\VtbVal}{calculations/flavor_geometry.tex}{VtbVal}

\subsection{The Unitary Matrix Representation}

The following matrix represents the global equilibrium of the flavor sector. Diagonal elements represent Persistence Efficiency, which scales super-linearly with the resonance tier.

\begin{equation}
|V_{CKM}| = 
\begin{pmatrix}
\VudVal & \CabibboSineVal & \VubVal \\
\CabibboSineVal & \VcsVal & \VcbVal \\
\VtdVal & \VtsVal & \VtbVal
\end{pmatrix}
\end{equation}

All values represent absolute magnitudes $|V_{ij}|$.

\subsection{Geometric Unitarity and Reciprocal Elements}

In the Standard Model, unitarity (\(V^{\dag }V=I\)) is a postulate. In the $E_8$-Persistence Theory, it is a consequence of \textbf{State Saturation}. Because the chiral state space is limited to $\nu=16$ channels, the Unitary Probability Conservation follows from saturated state-space logic: probability cannot be lost, only re-routed.

\subsubsection{Conservation of Interference}
The off-diagonal elements are not independent variables; they are the geometric consequences of enforcing unitary closure on a twisted lattice. Because the Chiral Projection Operator introduces a phase offset ($\delta \approx 68^\circ$), the transition amplitudes between generations behave as complex vectors rather than scalars. This results in \textbf{Geometric Interference} patterns that dictate the secondary hierarchy.

\begin{itemize}
    \item \textbf{Unitary Reflection ($V_{cd}$):} The transition $c \to d$ mirrors the primary Cabibbo leak. However, strictly preserving unitarity requires the vector sum of the direct path and the cross-generation loop:
    \begin{equation}
    |V_{cd}| = \VcdEq
    \end{equation}
    
    \item \textbf{Destructive Interference ($V_{td}$):} The transition $t \to d$ is heavily suppressed not merely by distance, but by geometry. The two available pathways for this transition ($1\to 2 \to 3$ vs $1 \to 3$) possess a relative phase difference driven by $\delta$. This results in a vector subtraction that cancels a significant portion of the amplitude:
    \begin{equation}
    |V_{td}| = \VtdEq
    \end{equation}
    This geometric cancellation explains the extreme suppression of $V_{td}$ without requiring arbitrary tuning.
    
    \item \textbf{Constructive Persistence ($V_{ts}$):} Similarly, the $t \to s$ transition is defined by the interference of the remaining unitarity triangle vector:
    \begin{equation}
    |V_{ts}| = \VtsEq
    \end{equation}
\end{itemize}

\subsubsection{Diagonal Persistence}
The diagonal elements ($V_{ud}, V_{cs}, V_{tb}$) represent the \textbf{Geometric Stiffness} of the generation—the probability that a topological knot retains its identity against the vacuum flux. These are calculated strictly as the unitarity residual:
\begin{equation}
|V_{ii}| = \sqrt{1 - \sum_{j \neq i} |V_{ij}|^2}
\end{equation}
This derivation reduces the degrees of freedom of the CKM matrix from 4 empirical parameters to 0, as all elements are generated entirely from the primary geometric transitions ($\pi/14$, etc.) and the saturation constraint.

\subsection{The CP-Violating Phase: Geometric Diode Offset}

In the Standard Model, the CP-violating phase ($\delta_{CP}$) is a free parameter required to explain the asymmetry between matter and antimatter. In the $E_8$-Persistence Theory, this phase is derived as the necessary angular offset of the \textbf{Chiral Projection Operator}.

\subsubsection{The Chiral Truncation Mechanism}
As established in Paper I, the causal arrow of time is enforced by truncating the total lattice degrees of freedom ($N=32$) to the chiral state space rank ($\nu=16$). This truncation breaks the parity symmetry of the substrate. However, the lattice retains its fundamental 5-fold rotational symmetry ($\sigma=5$) in the projection, while the particle nodes retain their 2-point topological boundaries ($\chi=2$).

\subsubsection{The Geometric Phase Derivation}
The CP phase $\delta$ corresponds to the geometric angle between the Lattice Symmetry vector ($\sigma$) and the Topological Boundary vector ($\chi$) in the projection space. Geometrically, the phase lag is defined as the angle whose tangent is the ratio of the rotational freedom to the boundary lock:

\begin{equation}
\delta = \arctan\left(\frac{\sigma}{\chi}\right) = \arctan\left(\frac{5}{2}\right)
\end{equation}

\subsubsection{Numerical Result}
\begin{equation}
\delta \approx 68.1986^\circ
\end{equation}

\begin{itemize}
    \item \textbf{Experimental Target:} $68.2^\circ \pm 4.5^\circ$ (Particle Data Group)
    \item \textbf{Accuracy:} Matches the experimental central value to within $0.01^\circ$.
\end{itemize}

\textbf{Physical Interpretation:} CP violation is not an arbitrary force; it is the Topological Phase Offset of the Chiral Projection Operator. The universe cannot maintain both causality (Chiral Truncation) and perfect CP symmetry simultaneously. The phase $\delta$ is the invariant geometric signature of this broken symmetry.


% --- Dynamic Tags for Benchmarks ---
\CatchFileBetweenTags{\AngleGammaVal}{calculations/flavor_geometry.tex}{AngleGammaVal}
\CatchFileBetweenTags{\AngleGammaEq}{calculations/flavor_geometry.tex}{AngleGammaEq}
\CatchFileBetweenTags{\AngleGammaExp}{calculations/flavor_geometry.tex}{AngleGammaExperimentalValue}
\CatchFileBetweenTags{\AngleGammaSig}{calculations/flavor_geometry.tex}{AngleGammaSigma}

\CatchFileBetweenTags{\SinTwoBetaVal}{calculations/flavor_geometry.tex}{Sin2BetaVal}
\CatchFileBetweenTags{\SinTwoBetaEq}{calculations/flavor_geometry.tex}{Sin2BetaEq}
\CatchFileBetweenTags{\SinTwoBetaExp}{calculations/flavor_geometry.tex}{Sin2BetaExperimentalValue}
\CatchFileBetweenTags{\SinTwoBetaSig}{calculations/flavor_geometry.tex}{Sin2BetaSigma}

\CatchFileBetweenTags{\WolfLambdaVal}{calculations/flavor_geometry.tex}{WolfLambdaVal}
\CatchFileBetweenTags{\WolfAVal}{calculations/flavor_geometry.tex}{WolfAVal}
\CatchFileBetweenTags{\WolfRhoVal}{calculations/flavor_geometry.tex}{WolfRhoVal}
\CatchFileBetweenTags{\WolfEtaVal}{calculations/flavor_geometry.tex}{WolfEtaVal}

\subsection{Precision Benchmarks: The Unitarity Triangle}

To validate that the geometric phase $\delta \approx 68.2^\circ$ is indeed the physical source of CP violation observed in collider experiments, we derive the standard Unitarity Triangle observables and the Wolfenstein parameters directly from the lattice geometry.

\subsubsection{The B-Physics Angles (\texorpdfstring{$\gamma$ and $\beta$}{gamma and beta})}
The angles of the Unitarity Triangle ($\alpha, \beta, \gamma$) are phase differences between specific CKM matrix elements. The angle $\gamma$ (or $\phi_3$) is of particular interest as it corresponds directly to the phase of $V_{ub}$.

\begin{itemize}
    \item \textbf{Angle $\gamma$ (The Geometric Phase):} derived from the interference of the first and second generations.
    \begin{equation}
    \gamma = \AngleGammaEq \approx \AngleGammaVal
    \end{equation}
    \textbf{Experimental Status:} Matches the HFLAV world average \AngleGammaExp \ (\AngleGammaSig$\sigma$). This confirms that the derived lattice twist is the physical angle $\gamma$.

    \item \textbf{Sin($2\beta$) (The Gold Standard):} The precision observable measured via $B^0 \to J/\psi K_S$ decays.
    \begin{equation}
        \SinTwoBetaEq \approx \SinTwoBetaVal
    \end{equation}
    \textbf{Experimental Status:} Matches the HFLAV world average \SinTwoBetaExp \ within \SinTwoBetaSig$\sigma$. This high-precision agreement confirms that the vector subtraction logic used to derive $V_{td}$ accurately captures the interference patterns of the physical vacuum.
\end{itemize}

\subsubsection{Geometric Wolfenstein Parameters}
Standard phenomenology parameterizes the CKM matrix using the Wolfenstein expansion in powers of $\lambda = |V_{us}|$. We reverse-engineer these parameters from our exact geometric matrix to demonstrate compatibility.

\begin{align}
    \lambda &= |V_{us}| = \WolfLambdaVal \\
    A &= |V_{cb}| / \lambda^2 = \WolfAVal \\
    \bar{\rho} &= \text{Re}\left(\frac{V_{ub}}{A\lambda^3}\right) = \WolfRhoVal \\
    \bar{\eta} &= \text{Im}\left(\frac{V_{ub}}{A\lambda^3}\right) = \WolfEtaVal
\end{align}

\textit{Note: The deviation in $\bar{\rho}$ and $\bar{\eta}$ compared to global fits arises because the Wolfenstein parametrization is an $O(\lambda^3)$ approximation, whereas the lattice derivation is exact to all orders.}



\subsection{The Jarlskog Invariant: The Informational Cost of Causality}

The Jarlskog Invariant ($J$) is a rephasing-invariant measure of CP violation strength. In Informational Energetics, $J$ represents the Total Dissipative Cross-Section of the Chiral Projection Operator.

\subsubsection{Structural Consistency Check}
In Paper I (System IV-D), we derived the Jarlskog Invariant directly from the projection frustration of the 5-fold symmetry ($\phi^2$) acting on the temporal cost ($T_{geo}$):

\begin{equation}
J_{geo} = (\phi^2 \cdot \eta) \cdot T_{geo} \approx 3.08490 \times 10^{-5}
\end{equation}

We calculate $J$ via the CKM matrix product derived above to check for internal consistency:
\begin{equation}
J_{CKM} = |V_{us}| \cdot |V_{cb}| \cdot |V_{ub}| \cdot \sin(\delta)
\end{equation}
Substituting the derived geometric values:
\begin{equation}
\begin{split}
J_{CKM} &\approx (0.2244) \cdot (0.0413) \cdot (0.0036) \cdot \sin(68.2^\circ) \\
        &\approx 3.09 \times 10^{-5}
\end{split}
\end{equation}

The agreement between the direct projection derivation (Paper I) and the matrix product derivation (Paper III) confirms that the CKM matrix is the mechanical implementation of the vacuum's fundamental Time Asymmetry constraint.