\CatchFileBetweenTags{\JarlskogMatrixEq}{calculations/flavor_geometry.tex}{JarlskogMatrixEq}
\CatchFileBetweenTags{\JarlskogMatrixVal}{calculations/flavor_geometry.tex}{JarlskogMatrixVal}
\CatchFileBetweenTags{\JarlskogMatrixAccText}{calculations/flavor_geometry.tex}{JarlskogMatrixAccText}
\CatchFileBetweenTags{\JarlskogGeoVal}{calculations/flavor_geometry.tex}{JarlskogGeoVal}
\CatchFileBetweenTags{\JConsistencyPct}{calculations/flavor_geometry.tex}{JConsistencyPct}

\CatchFileBetweenTags{\AngleGammaEq}{calculations/flavor_geometry.tex}{AngleGammaEq}
\CatchFileBetweenTags{\AngleGammaVal}{calculations/flavor_geometry.tex}{AngleGammaVal}
\CatchFileBetweenTags{\AngleGammaAccText}{calculations/flavor_geometry.tex}{AngleGammaAccText}

\CatchFileBetweenTags{\SinTwoBetaVal}{calculations/flavor_geometry.tex}{SinTwoBetaVal}
\CatchFileBetweenTags{\SinTwoBetaEq}{calculations/flavor_geometry.tex}{SinTwoBetaEq}
\CatchFileBetweenTags{\SinTwoBetaAccText}{calculations/flavor_geometry.tex}{SinTwoBetaAccText}

\section{CP Violation \& The Entropic Cost of Causality}

\subsection{The Jarlskog Invariant (\texorpdfstring{$J$}{J})}
Under the rule of Reversible Encoding, the geometric mismatch of projecting 5-fold $H_4$ symmetry onto a 4-dimensional manifold cannot be erased; it is stored as the thermodynamic friction of the causal projection. The Jarlskog Invariant ($J$) measures this exact dissipative cross-section.

In Paper III, we established the projection frustration as $J_{geo} = (\phi^2 \cdot \eta) \cdot T_{geo} = \JarlskogGeoVal$, where $\phi = (1+\sqrt{5})/2$ is the Golden Ratio inherently generated by projecting the 5-fold internal symmetry ($\sigma=5$, $H_4$ Coxeter group) onto the 4D spacetime manifold. Calculating the invariant directly from our derived CKM matrix yields:

\begin{equation}
    J_{CKM} = \JarlskogMatrixEq = \JarlskogMatrixVal
\end{equation}
This value \JarlskogMatrixAccText The $\JConsistencyPct\%$ difference between the continuous bulk geometry and the discrete matrix calculation is the exact \textbf{Quantization Tax} of projecting $H_4$ symmetry onto integer channels.




\section{CP Violation and the Entropic Cost of Causality}

Under the rules of $E_8$-Persistence, the irreducible geometric mismatch of projecting a higher-dimensional symmetry onto a lower-dimensional manifold cannot be erased; it must be stored as the measurable thermodynamic friction of the projection (Landauer's Principle). 

In the Standard Model, the Jarlskog Invariant ($J$) serves as a rephasing-invariant measure of CP violation, but its specific magnitude ($\sim 3 \times 10^{-5}$) lacks a structural explanation. In the $E_8$-Persistence theory, $J$ is identified exactly as this \textbf{Projection Frustration}. Time asymmetry arises directly from the interaction between the intrinsic entropic cost of causal state updates and the discrete geometry of the manifold projection.

\subsection{The Continuous Limit: Holographic Projection}

We first evaluate this frustration in the continuous limit, where the $E_8$ lattice structure is approximated by the continuous $H_4$ Coxeter symmetry (the 600-cell). 

A fundamental theorem of crystallography dictates that 5-fold icosahedral symmetries cannot perfectly, periodically tile a 4D discrete lattice. Projecting the 5-fold internal symmetry of the lattice ($\sigma = 5$) onto the 4-dimensional spacetime manifold ($D = 4$) creates a geometric area deficit. Because the continuous $H_4$ geometry is governed by the Golden Ratio, $\phi = (1+\sqrt{5})/2$, the eigenvalue of this projection deficit is exactly $\phi^2$.

The total ideal dissipative cross-section ($J_{ideal}$) is the fundamental causal Toll ($T_{geo}$, the entropic cost of a single state transition, derived in the substrate architecture) amplified by this Projection Frustration ($\phi^2$) and the coordinate overhead ($\eta$):

\begin{equation}
    J_{ideal} = (\phi^2 \cdot \eta) \cdot T_{geo} \approx \mathbf{\JarlskogGeoVal}
    \label{eq:jarlskog_ideal}
\end{equation}

This value represents the \textbf{bulk phonon perception} of CP violation, the continuous entropic drag expected if the lattice could maintain perfect $H_4$ symmetry without discrete quantization constraints.

\subsection{The Quantization Gap: The Discrete Evaluation}

The actual CKM matrix is not continuous; it is governed by the discrete topological boundaries ($\chi=2$) and integer channel apertures (e.g., $\pi/14$) derived in Section III. 

Evaluating the physical Jarlskog invariant directly from our geometrically derived CKM matrix elements yields:

\begin{equation}
\begin{split}
    J_{CKM} &= \JarlskogMatrixEq \\
    &\approx \mathbf{\JarlskogMatrixVal}
\end{split}
\end{equation}

Comparing the matrix-derived surface evaluation to the continuous bulk prediction reveals a strict mathematical boundary:

\begin{equation}
    \Delta_J = \frac{|J_{CKM} - J_{ideal}|}{J_{ideal}} \approx \mathbf{\JConsistencyPct\%}
\end{equation}

\begin{table}[h]
\centering
\caption{\textbf{CP Violation: Discrete vs. Continuous Geometry.} The comparison reveals a structural correspondence between the knot topology and the bulk geometry, separated by the quantization gap.}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{} l l l @{}}
\toprule
\textbf{Category} & \textbf{Surface} ($J_{CKM}$) & \textbf{Bulk} ($J_{ideal}$) \\
\midrule
\textbf{Value}    & $\mathbf{\JarlskogMatrixVal}$         & $\mathbf{\JarlskogGeoVal}$             \\
\textbf{Source}   & Unitary Matrix               & Golden Ratio                \\
\textbf{Details}  & ($\pi/14$, etc.)            & ($\phi^2 \cdot \eta \cdot T_{geo}$)           \\
\textbf{Type}     & Transcendental               & Algebraic                   \\
\midrule
\textbf{Deviation} & \multicolumn{2}{c}{\textbf{\JConsistencyPct\%} (Projection Entropy)} \\
\bottomrule
\end{tabular}
\label{tab:jarlskog_gap}
\end{table}

\subsection{Physical Interpretation: The Entropy of Discretization}

The $\sim 2\%$ discrepancy is not experimental error; both $J_{CKM}$ and $J_{ideal}$ are exact, parameter-free theoretical calculations. Rather, this gap quantifies the \textbf{Geometric Entropy} of discretization. It is the irreducible information loss incurred when forcing an irrational symmetry ($\phi$) onto a discrete integer lattice. It is the ``pixelation" of continuous geometry.

\begin{quote}
    \textit{CP violation is the projection of the lattice's entropic action onto the 4D chiral manifold. The physical observable ($J_{CKM}$) is subject to a $\sim 2\%$ quantization tax arising from the discretization of the continuous $H_4$ symmetry.}
\end{quote}

This correspondence makes a definitive, testable prediction: as experimental precision improves, the gap $\Delta_J$ must remain stable at $\approx 2\%$. It cannot shrink to zero (which would imply an impossible numerical coincidence between transcendental matrix products and algebraic numbers) nor can it widely diverge. The gap is the measurable, physical signature of the vacuum's discrete fabric.













\section{Corollary: The Geometric Origin of the Jarlskog Invariant}

Standard quantum mechanics defines the Jarlskog Invariant $J$ as twice the area of the Unitarity Triangle ($J = 2A$), representing the strict, basis-independent measure of CP violation. In the lattice model, this factor of 2 is not an arbitrary convention; it arises directly from the \textbf{Chiral Projection}. 

The area $A$ exists on the projected 4D manifold, but the invariant $J$ must account for the full informational bit-depth of the lattice node ($N=32$) relative to the chiral channel ($\nu=16$). The geometric area is strictly half the invariant phase space:
\begin{equation}
    A_{triangle} = \frac{J}{N/\nu} = \frac{J}{2}
\end{equation}
This identifies the Unitarity Triangle as the exact ``half-integer'' holographic projection of the substrate's CP-violating phase space.
