\section{The PMNS Matrix: Neutrino Mixing Protocol}

\subsection{The Fundamental Difference: Knots vs. Phonons}

The most striking feature of the flavor sector is the magnitude disparity between quark mixing (CKM) and neutrino mixing (PMNS). As established in \textbf{Paper II}, this is a consequence of the structural duality of the substrate:

\begin{enumerate}
    \item \textbf{Quarks are Topological Solitons ($\Delta^n$):} Constrained by Manifold Drag.
    \item \textbf{Neutrinos are Lattice Phonons ($\Delta^{-n}$):} Characterized by \textbf{Symmetry Transparency}.
\end{enumerate}

Because neutrinos are delocalized vibrations ($M \approx 9$ meV), they do not interact with the ``interface crack" ($\pi$) like quarks; they resonate across the global symmetry ratios of the lattice ($\sigma/\nu$). This explains why PMNS angles are large and geometric ($30^\circ, 45^\circ$) while CKM angles are small and frictional ($13^\circ$).

\subsection{The Solar Angle (\texorpdfstring{$\theta_{12}$}{theta12}): The Symmetry Ratio}

\textbf{The Problem:} How does a delocalized phonon distribute itself across the lattice substrate?

\textbf{The Geometric Derivation:} Unlike fermions which are restricted to specific integer channels, phonons resonate across the full Interaction Order ($\sigma$) relative to the Chiral Basis ($\nu$). This creates a distribution governed by the projection geometry of the lattice.

\subsubsection{First Order Approximation (Integer Hardware)}
At the bit-level of the lattice hardware, the mixing is defined by the integer ratio of the Symmetry Order to the Channel Capacity.

\begin{itemize}
    \item \textbf{Numerator ($\sigma = 5$):} The 5 interaction shells of the Petrie projection.
    \item \textbf{Denominator ($\nu = 16$):} The fundamental bit-depth of the chiral capacity.
\end{itemize}

\begin{equation}
\sin^2 \theta_{12} \approx \frac{\sigma}{\nu} = \frac{5}{16} = \mathbf{0.3125}
\end{equation}
\textit{(Error: 1.8\% relative to experiment)}

\CatchFileBetweenTags{\SolarAngleEq}{calculations/flavor_geometry.tex}{SolarAngleEq}
\CatchFileBetweenTags{\SolarAngleExp}{calculations/flavor_geometry.tex}{SolarAngleExperimentalValue}
\CatchFileBetweenTags{\SolarAngleAccText}{calculations/flavor_geometry.tex}{SolarAngleAccText}

\subsubsection{The Phonon Refinement (Golden Geometry)}
While the integer ratio provides a strong first approximation, neutrinos are lattice phonons (waves), not static knots. They couple to the \textit{continuous geometry} of the 4D projection rather than the discrete bits.

The projection of $E_8$ to 4D is governed by the $H_4$ Coxeter group (the 600-cell), where the 5-fold symmetry manifests continuously as the Golden Ratio ($\phi$). The exact geometric solution is the inverse of the Golden aperture:

\begin{equation}
\sin^2 \theta_{12} = \SolarAngleEq \approx \SolarAngleVal
\end{equation}

\begin{itemize}
    \item \textbf{Experimental Target:} \SolarAngleExp
    \item \textbf{Accuracy:} \SolarAngleAccText
\end{itemize}

\textbf{Physical Meaning:} The Solar angle is the ratio of Lattice Symmetry to Capacity. Neutrinos, being waves, ``see" the continuous Golden Geometry ($1/2\phi$) of the substrate, while Quarks ``see" the discrete Integer Channels ($5/16$).


\CatchFileBetweenTags{\NuCPVal}{calculations/flavor_geometry.tex}{NuCPVal}
\CatchFileBetweenTags{\NuCPEq}{calculations/flavor_geometry.tex}{NuCPEq}

\subsection{The Neutrino CP Phase (\texorpdfstring{$\delta_{CP}^\nu$}{deltacpnu}): The Golden Angle}

While the Quark CP phase is determined by the discrete topological boundary of the lattice ($\delta_{q} \approx \arctan(5/2) \approx 68.2^{\circ}$), neutrinos resonate with the continuous bulk geometry of the 4D projection. As established in the Solar Angle derivation, this bulk geometry is governed by the $H_4$ Coxeter group and the Golden Ratio ($\phi$).

Consequently, the CP-violating phase for neutrinos is not the discrete ``Diode Offset,'' but the continuous \textbf{Golden Angle}, the fundamental geometric proportion of the circle divided by $\phi$:

\begin{equation}
\delta_{CP}^\nu = \NuCPEq \approx \NuCPVal
\label{eq:neutrino_cp}
\end{equation}

This geometric prediction lies within the $1\sigma$ likelihood region of the global best fit provided by NuFIT 5.3 for Normal Ordering ($\delta_{CP} \approx 230^{\circ}$). This distinguishes the $E_8$ lattice prediction from the maximal CP violation ($270^{\circ}$) often assumed in early T2K analyses.

\begin{center}
\begin{tabular}{l c c}
\hline
\textbf{Parameter} & \textbf{Geometric Derivation} & \textbf{Value} \\
\hline
Quark Phase ($\delta_{CKM}$) & Discrete Diode ($\arctan \frac{\sigma}{\chi}$) & $68.2^{\circ}$ \\
Neutrino Phase ($\delta_{PMNS}$) & Golden Angle ($2\pi / \phi$) & $222.5^{\circ}$ \\
\hline
\end{tabular}
\end{center}







\subsection{The Atmospheric Angle (\texorpdfstring{$\theta_{23}$}{theta23}): The Boundary Limit}

\textit{The Problem:} What is the maximum mixing entropy allowed by the topology?

\textit{The Geometric Derivation:} The mixing between the second and third generations represents the maximal delocalization allowed by the Topological Boundary ($\chi$).

\begin{itemize}
    \item \textbf{Constraint ($\chi = 2$):} From the Mapping Function, $\chi$ is the Euler characteristic defining the node.
    \item \textbf{The Limit:} In a system with a 2-point boundary, the maximum Shannon entropy state is an equal partition ($1/2$).
\end{itemize}

\begin{equation}
\sin^2 \theta_{23} = \frac{1}{\chi} = \frac{1}{2} = \mathbf{0.5000}
\end{equation}

\begin{itemize}
    \item \textbf{Experimental Target (NuFIT 5.3):} $0.51 \pm 0.03$ (Normal Hierarchy)
    \item \textbf{Accuracy:} 98.0\%
    \item \textbf{Physical Meaning:} This is Maximal Mixing. The $\chi=2$ boundary allows equal probability distribution between the $\mu$ and $\tau$ sectors. This explains why $\theta_{23}$ is close to $45^\circ$ while quark angles are small; quarks are constrained by the Manifold Drag ($\pi$), while neutrinos are constrained only by the Topology ($\chi$).
\end{itemize}

\subsection{The Reactor Angle (\texorpdfstring{$\theta_{13}$}{theta13}): The Interaction Leak}

\textit{The Problem:} Why is $\theta_{13}$ non-zero but small?

\textit{The Geometric Derivation:} This angle represents the leakage of the Interaction Remainder ($\sigma - \chi = 3$) into the neutrino sector. Although neutrinos are colorless, as \textbf{Global Phonons} they propagate through the bulk lattice structure. They inevitably scatter off the geometric pillars that support color charge, scaled by the vacuum impedance.

\begin{itemize}
    \item \textbf{Numerator ($\sigma - \chi = 3$):} The \textbf{Interaction Remainder} derived in Paper I. This is the specific structural invariant that mandates exactly three quark colors and three fermion generations.
    \item \textbf{Denominator ($\alpha^{-1} \approx 137$):} The Vacuum Impedance.
\end{itemize}

\begin{equation}
\sin^2 \theta_{13} = \frac{\sigma - \chi}{\alpha^{-1}} = \frac{3}{137.036} \approx \mathbf{0.02189}
\end{equation}

\begin{itemize}
    \item \textbf{Experimental Target (NuFIT 5.3):} $0.0220 \pm 0.0006$
    \item \textbf{Accuracy:} 99.5\%
    \item \textbf{Physical Meaning:} The Reactor angle quantifies the structural cross-talk between the Color Sector (3) and the Vacuum Field ($\alpha^{-1}$). It proves that the ``3" appearing in the PMNS matrix is the same ``3" that defines the number of generations and colors, linked by the global coherence of the lattice phonon.
\end{itemize}

The complete derivation of the neutrino sector is summarized in Table \ref{tab:pmns_derivation}. The agreement across all four parameters ($\theta_{12}, \theta_{23}, \theta_{13}, \delta_{CP}$) confirms that the PMNS matrix is not random, but follows the harmonic resonance logic of the $E_8$ substrate.



\subsection{Geometric Predictions}

The identification of neutrinos as Lattice Phonons rather than topological knots imposes strict constraints on their physical behavior, distinct from standard field theory expectations.

\begin{enumerate}
    \item \textbf{Neutrino Mass Hierarchy (Normal Ordering):}
    \begin{itemize}
        \item \textbf{Prediction:} The JUNO (2026) and DUNE experiments will confirm the Normal Hierarchy ($m_1 < m_2 < m_3$).
        \item \textbf{Mechanism:} The system fills volumetric resonances from the ground state upward. An Inverted Hierarchy ($m_3 < m_1$) would imply a ``Topological Debt" where higher-order lattice excitations exist without the foundational support of the lower tiers, violating the Lagrangian of Persistence.
    \end{itemize}

    \item \textbf{The Cosmological Mass Discrepancy:}
    \begin{itemize}
        \item \textbf{Prediction:} While oscillation experiments measure the Protocol Latency (friction), the Euclid Satellite (2026) will measure the Structural Rest Mass, settling on a sum significantly below the current $60 \text{ meV}$ floor (predicted $\Sigma m_\nu \approx 0.20 \text{ meV}$).
        \item \textbf{Mechanism:} Because phonons decouple from the Manifold Drag ($\pi D$), their gravitational mass (rest mass) is orders of magnitude lower than their inertial resistance to flavor change (oscillation mass). This discrepancy is the signature of a Phonon-based neutrino sector.
    \end{itemize}
\end{enumerate}

% --- Load Dynamic Constants for PMNS ---
\CatchFileBetweenTags{\SolarAngleVal}{calculations/flavor_geometry.tex}{SolarAngleVal}
\CatchFileBetweenTags{\SolarAngleEq}{calculations/flavor_geometry.tex}{SolarAngleEq}
\CatchFileBetweenTags{\SolarAngleExp}{calculations/flavor_geometry.tex}{SolarAngleExperimentalValue}
\CatchFileBetweenTags{\SolarAngleSig}{calculations/flavor_geometry.tex}{SolarAngleSigma}

\CatchFileBetweenTags{\AtmosAngleVal}{calculations/flavor_geometry.tex}{AtmosAngleVal}
\CatchFileBetweenTags{\AtmosAngleEq}{calculations/flavor_geometry.tex}{AtmosAngleEq}
\CatchFileBetweenTags{\AtmosAngleExp}{calculations/flavor_geometry.tex}{AtmosAngleExperimentalValue}
\CatchFileBetweenTags{\AtmosAngleSig}{calculations/flavor_geometry.tex}{AtmosAngleSigma}

\CatchFileBetweenTags{\ReactorAngleVal}{calculations/flavor_geometry.tex}{ReactorAngleVal}
\CatchFileBetweenTags{\ReactorAngleEq}{calculations/flavor_geometry.tex}{ReactorAngleEq}
\CatchFileBetweenTags{\ReactorAngleExp}{calculations/flavor_geometry.tex}{ReactorAngleExperimentalValue}
\CatchFileBetweenTags{\ReactorAngleSig}{calculations/flavor_geometry.tex}{ReactorAngleSigma}

\CatchFileBetweenTags{\NuCPVal}{calculations/flavor_geometry.tex}{NuCPVal}
\CatchFileBetweenTags{\NuCPEq}{calculations/flavor_geometry.tex}{NuCPEq}
\CatchFileBetweenTags{\NuCPExp}{calculations/flavor_geometry.tex}{NuCPExperimentalValue}
\CatchFileBetweenTags{\NuCPSig}{calculations/flavor_geometry.tex}{NuCPSigma}

\begin{table*}[h]
\centering
\caption{\textbf{Derivation of PMNS Matrix Elements.} Geometric predictions for neutrino mixing compared to NuFIT 5.3 global fit values. Unlike quarks, neutrinos follow global symmetry ratios ($\phi, \chi$) rather than interface apertures.}
\label{tab:pmns_derivation}
\renewcommand{\arraystretch}{1.8} 
\setlength{\tabcolsep}{5pt}
\begin{tabular}{@{} l l l c c r @{}} 
\toprule
\textbf{Parameter} & \textbf{Symbol} & \textbf{Geometric Logic} & \textbf{Predicted} & \textbf{Target (NuFIT)} & \textbf{Dev.} \\
\midrule
Solar Angle & $\sin^2 \theta_{12}$ & Golden Ratio Aperture ($\SolarAngleEq$) & \textbf{\SolarAngleVal} & \SolarAngleExp & $+\SolarAngleSig\sigma$ \\
Atmospheric & $\sin^2 \theta_{23}$ & Boundary Limit ($\AtmosAngleEq$) & \textbf{\AtmosAngleVal} & \AtmosAngleExp & $-\AtmosAngleSig\sigma$ \\
Reactor & $\sin^2 \theta_{13}$ & Interaction Leak ($\ReactorAngleEq$) & \textbf{\ReactorAngleVal} & \ReactorAngleExp & $-\ReactorAngleSig\sigma$ \\
CP Phase & $\delta_{CP}^\nu$ & The Golden Angle ($\NuCPEq$) & \textbf{\NuCPVal} & \NuCPExp & $-\NuCPSig\sigma$ \\
\bottomrule
\end{tabular}
\end{table*}