\CatchFileBetweenTags{\UnityGapVal}{calculations/flavor_geometry.tex}{UnityGapVal}
\CatchFileBetweenTags{\UnityGapEq}{calculations/flavor_geometry.tex}{UnityGapEq}
\CatchFileBetweenTags{\GSTGapPct}{calculations/flavor_geometry.tex}{GSTGapPct}
\CatchFileBetweenTags{\CabibboSineVal}{calculations/flavor_geometry.tex}{CabibboSineVal}
\CatchFileBetweenTags{\MassRatioVal}{calculations/flavor_geometry.tex}{MassRatioVal}
\CatchFileBetweenTags{\MassRatioEq}{calculations/flavor_geometry.tex}{MassRatioEq}
\CatchFileBetweenTags{\GapTwoThreeVal}{calculations/flavor_geometry.tex}{GapTwoThreeVal}
\CatchFileBetweenTags{\GapTwoThreeEq}{calculations/flavor_geometry.tex}{GapTwoThreeEq}
\CatchFileBetweenTags{\AlphaInvVal}{calculations/constants.tex}{AlphaInvVal}

\section{The Gauge-Flavor Connection: Impedance Matching}

In standard QFT, the gauge sector (which dictates forces) and the flavor sector (which dictates masses and mixing) are treated as fundamentally disconnected. Their couplings and mixing angles are independent empirical inputs. In the $E_8$-Persistence theory, they are structurally coupled: both sectors must partition the exact same finite $\nu=16$ channel capacity while minimizing total Entropic Action.


\subsection{Mixing Geometry Dictates Mass Hierarchies}

Standard phenomenology assumes that arbitrary Higgs Yukawa couplings generate mass matrices, which are subsequently diagonalized to yield the mixing angles. We propose \textbf{The Geometric Priority Principle:} The rigid transition geometry of the discrete substrate is the primary constraint. The observed mass hierarchies are the self-organized spectrum that satisfies these mixing apertures, not the generators of them.

To maintain a persistent vacuum state, the transfer of coordinate information across generational boundaries must minimize local Entropic Action ($\mathcal{D} = \xi \cdot \mathbf{K} \cdot f$). Minimizing this signal reflection requires satisfying the \textbf{Resonant Impedance Matching Filter}. At a chiral lattice interface, the transmission coefficient $\mathcal{T}$ relates to the kinematic impedance (mass) ratio:
\begin{equation}
    \mathcal{T} \approx \sin^2 \theta \quad \text{and} \quad \frac{Z_1}{Z_2} \approx \frac{m_{\text{light}}}{m_{\text{heavy}}}
\end{equation}
In the limit where the generational boundary acts as a matched load between distinct resonant tiers, the transmission coefficient for coordinate information reduces to the geometric overlap $\sin^2\theta$ [2]. The impedance ratio $Z_1/Z_2$ maps to the mass ratio because rest mass is the topological impedance arresting propagation (Section IV.D of [2]).

To achieve stable, non-reflective power transfer, maximum efficiency occurs when the coupling geometry matches the geometric mean of the impedances:
\begin{equation}
    \theta_{\text{optimal}} \approx \sqrt{\frac{m_{\text{light}}}{m_{\text{heavy}}}}
    \label{eq:resonant_filter}
\end{equation}
We apply this resonant filter as a strict boundary condition governing the self-organization of the emergent mass spectrum.

\subsection{Type I Boundaries: The GST Relation as a Chiral Filter}

For adjacent transitions between the first and second generations (e.g., $u \leftrightarrow s$), the transition is a \textbf{Type I Chiral Leak} restricted entirely to the active boundary. This constrains the transmission aperture strictly to the boundary geometry derived in Section III.B ($\sin\theta_C = \pi/14 \approx \CabibboSineVal$). 

To satisfy the resonant impedance matching filter (Eq.~\ref{eq:resonant_filter}) across this boundary, the mass ratio of the light quarks must converge to match this aperture:
\begin{equation}
    \sqrt{\frac{m_d}{m_s}} \approx \sin\theta_C = \frac{\pi}{14}
\end{equation}
This geometric derivation identifies the historical 1968 Gatto-Sartori-Tonin (GST)~\cite{gatto_weak_1968} relation as a consequence of resonant impedance matching at the chiral boundary.

\begin{table}[h]
\centering
\caption{The GST relation emerges as a consistency condition of resonant impedance matching.}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{} l c c c @{}}
\toprule
\textbf{Observable} & \textbf{Value} & \textbf{Source} & \textbf{Error} \\
\midrule
Geometric Aperture ($\sin\theta_C$) & $\mathbf{0.2244}$ & Theory ($\pi/14$) & -- \\
Mass Impedance ($\sqrt{m_d/m_s}$) & $\mathbf{0.2236}$ & PDG Data & $\mathbf{0.4\%}$ \\
\bottomrule
\end{tabular}
\label{tab:gst_validation}
\end{table}

\subsection{Type II Boundaries: The Volumetric Mass Aperture}

While the GST relation is highly accurate for the light generations, it does not extend to heavier quarks, where the mass ratio $\sqrt{m_s/m_b} \approx 0.15$ diverges from the mixing parameter $|V_{cb}| \approx 0.041$. 

This breakdown is explained by the distinct geometric character of Type II transitions. Transitions to the third generation (e.g., $s \to b$) are \textbf{Type II Dimensional Shifts} representing a promotion from an areal to a volumetric resonance. The capacity footprint expands from the 2D chiral boundary into the 3D internal interaction bulk, meaning the wave must scale with both the chiral channels ($\nu=16$) and the interaction symmetry order ($\sigma=5$). The corresponding \textbf{volumetric mass aperture} is:
\begin{equation}
    \theta_{\text{bulk}} = \GapTwoThreeEq = \frac{\pi}{21} \approx \GapTwoThreeVal
\end{equation}

Using the experimental bottom quark mass as an empirical anchor ($m_b \approx 4183$~MeV)~\cite{navas_review_2024}, the geometric cascade predicts the strange quark mass as $m_s = m_b (\pi/21)^2 \approx 93.54$~MeV—agreeing with the experimental MS-bar mass ($93.5 \pm 0.8$~MeV)~\cite{navas_review_2024} to within $0.1\%$. Cascading these apertures likewise characterizes the down quark mass: $m_d = m_s (\pi/14)^2 \approx 4.71$~MeV. 

The geometry distinguishes static mass scales from dynamic mixing amplitudes: while mass scales are determined purely by relative geometric apertures ($\pi/14$ and $\pi/21$), mixing transitions require a physical wave state to propagate across these boundaries, engaging the bulk vacuum. Because the active, dynamical transition into the volumetric bulk must overcome the fundamental impedance of the vacuum field ($\alpha^{-1} \approx 137$), the resulting mixing amplitude is heavily suppressed ($|V_{cb}| \propto 1/\alpha^{-1} \approx 0.041$) relative to the static mass ratio. The geometry thus uniquely specifies where the simple mass-mixing relation applies ($\pi/14$), where the mass ratio scales to the bulk ($\pi/21$), and where the vacuum impedance decouples the mixing angle.

\subsection{The Lepton Protected Identity}

If geometric impedance matching forces quarks to mix, why does the charged lepton mixing matrix remain the identity matrix (zero mixing)? 

Quarks are \textbf{Topological Solitons}: localized boundary structures anchored to the spacetime manifold by Manifold Drag ($\pi D$), incurring CKM leakage when re-spliced across generations.

Charged leptons are \textbf{Global Architectures}: their quantum numbers are defined by the full lattice symmetry rather than a localized boundary. Lacking the $\pi D$ topological anchor, they experience no boundary friction and their flavor matrix remains the identity.

Because leptons lack the $\pi D$ Manifold Drag that localizes quarks to the boundary, no energy barrier separates generational states, and their flavor matrix remains exactly diagonal.

\subsection{Structural Unification: The Capacity Coupling Identity}

The empirical similarity between the Weak Mixing Angle ($\sin^2\theta_W \approx 0.223$) and the Cabibbo Angle ($\sin\theta_C \approx 0.225$) lacks a first-principles explanation in standard phenomenology. In the $E_8$-Persistence framework, this alignment is a \textbf{structural consequence} of Capacity Partitioning on a single $\nu=16$ hardware ledger.

We first establish an exact algebraic identity between the boundary flavor width and the bulk transition capacity:
\begin{equation}
    \frac{\nu - \chi}{\nu + \sigma} = \frac{14}{21} = \frac{2}{3} = \frac{\chi}{\sigma - \chi}
\end{equation}
This $2:3$ ratio is dictated by the substrate geometry; it is the fundamental ratio of the topological boundary ($\chi=2$) to the interaction bulk remainder ($\sigma-\chi=3$), and it is the same ratio underlying the QCD screening coefficient ($\beta_0 = 11 - \frac{2}{3}n_f$) derived in Paper III.

The Weak Mixing Angle partitions the total system capacity $N_{sys} = D\Delta + \nu\eta + \sigma$ (Section VI.E). Using the exact capacity identity to substitute $\nu + \sigma = \frac{3}{2}(\nu - \chi)$, and noting that the Cabibbo angle fixes the boundary aperture as $\sin\theta_C = \pi/(\nu - \chi)$, we obtain the exact \textbf{Electroweak-Flavor Coupling Equation}:
\begin{equation}
    \sin^2\theta_W = \frac{\Delta}{D\Delta + \frac{3\pi\eta}{2\sin\theta_C} + (1-\eta)\sigma}
\end{equation}
where $\eta = (D\Delta-1)/(D\Delta) \approx 0.994186$ is the deterministic coordinate overhead correction.

In the limit of negligible coordinate overhead ($\eta \to 1$), this relation simplifies to:
\begin{equation}
    \sin^2\theta_W \approx \frac{1}{D + \frac{3\pi}{2\Delta\sin\theta_C}}
\end{equation}
Evaluating this approximate form with the substrate invariants yields $\sin^2\theta_W \approx 0.2235$, confirming that the gauge partition of spacetime and the generational transition leak of the boundary are algebraically coupled branches of a single capacity ledger. The $\mathcal{O}(1-\eta) \approx 0.6\%$ correction from finite coordinate resolution yields the precise prediction of Section VI.E.