\section{Discussion}

\subsection{Systemic Constraints and No-Go Theorems}

The $E_8$-Persistence Theory enforces strict topological limits on field behavior, providing solutions to long-standing "fine-tuning" mysteries by identifying them as architectural requirements.

\subsubsection{1. Prohibition of Neutrinoless Double Beta Decay ($0\nu\beta\beta$)}

Standard physics often invokes \textbf{Majorana masses} and the \textbf{See-saw Mechanism} to explain the extreme lightness of neutrinos relative to the charged leptons. This requires the existence of yet-undiscovered, ultra-heavy right-handed neutrinos.

The $E_8$-Persistence Theory achieves the same mass suppression without additional particles. Neutrino mass scales via \textbf{Inverse Resonance Scaling} ($1/\Delta^n$), where the "lightness" is a direct function of the lattice's resonant depth. In this framework, the See-saw mechanism is a mathematical artifact; the "heavy" side of the balance is not a particle, but the \textbf{Heegner Constant ($\Delta$)} itself.

\begin{itemize}
    \item \textbf{The Constraint:} Because the \textbf{Chiral Diode} establishes a strictly directional signal flow, a vibration cannot be its own reflection. Majorana nature is architecturally prohibited.
    \item \textbf{The Decisive Test:} This represents a "Hard Falsification" point for the model. The observation of neutrinoless double-beta decay by experiments like LEGEND or nEXO would invalidate the Chiral Diode architecture and the $E_8$ substrate logic.
\end{itemize}

\subsubsection{2. Structural Resonance: The Golden Cost of Time}

We observe a striking geometric relationship between the magnitude of CP Violation ($J$, derived in this paper) and the Vacuum Temporal Tax ($T$, derived in Paper I).

\begin{equation}
\frac{J}{T} = \frac{3.09 \times 10^{-5}}{1.185 \times 10^{-5}} \approx \mathbf{2.61}
\end{equation}

This ratio aligns with the Squared Golden Ratio ($\phi^2 \approx 2.618$) to within 0.4\%.

\textbf{Physical Interpretation:}
\begin{itemize}
    \item $T$ is the metabolic cost of a linear time step.
    \item $J$ is the informational asymmetry required to distinguish "forward" from "backward."
    \item The relationship $J \approx \phi^2 T$ implies that Time Asymmetry is the icosahedral projection of the Metabolic Cost.
\end{itemize}

Just as a 3D object casts a 2D shadow, the metabolic cost of the 8D lattice casts a "Golden Shadow" onto the 4D manifold. That shadow is CP violation.

\subsection{Summary of Flavor Observables}

To validate the CKM matrix derivation, we compare the resulting geometric angles and invariants against the latest experimental benchmarks. This "Flavor Series" represents the geometric bridge between the $E_8$ lattice and physical observables:

\begin{itemize}
    \item \textbf{Cabibbo Angle ($\theta_C$):} Derived as the geometric slope of the generation interface ($\arcsin(\pi / 14)$).
    \begin{itemize}
        \item \textbf{Prediction:} $\mathbf{13.0^\circ}$
        \item \textbf{Experimental Target (PDG):} $13.0^\circ$
        \item \textbf{Status:} Perfect Agreement.
    \end{itemize}

    \item \textbf{CP-Phase ($\delta$):} Derived as the angular offset of the Chiral Diode ($\arctan(5/2)$).
    \begin{itemize}
        \item \textbf{Prediction:} $\mathbf{68.20^\circ}$
        \item \textbf{Experimental Target (PDG):} $68.2^\circ$
        \item \textbf{Status:} Perfect Agreement.
    \end{itemize}

    \item \textbf{Jarlskog Invariant ($J$):} Derived as the total dissipative cross-section ($\prod V_{ij} \sin \delta$).
    \begin{itemize}
        \item \textbf{Prediction:} $\mathbf{3.09 \times 10^{-5}}$
        \item \textbf{Experimental Target (PDG):} $3.08 \times 10^{-5}$
        \item \textbf{Status:} 99.7\% Match.
    \end{itemize}
\end{itemize}

\textbf{Interpretation:} The precision of these benchmarks confirms that flavor mixing is a \textbf{Rotational Operator} within the lattice hardware. The Cabibbo angle is the geometric slope of the Gen-1/Gen-2 joint, while the CP-phase is the angular offset of the Chiral Diode.
