\CatchFileBetweenTags{\AtmosAngleVal}{calculations/flavor_geometry.tex}{AtmosAngleVal}
\CatchFileBetweenTags{\JarlskogMatrixVal}{calculations/flavor_geometry.tex}{JarlskogMatrixVal}
\CatchFileBetweenTags{\NuCPVal}{calculations/flavor_geometry.tex}{NuCPVal}

\section{Falsification Criteria and Experimental Audits}

The complete absence of empirical tuning parameters renders these derivations strictly falsifiable. Any future precision data that conclusively shifts the experimental central values outside the theoretical limits defined by these invariant ratios would directly falsify the underlying substrate. We identify four primary experimental audits and hard constraints, ordered by their observational immediacy:

\begin{enumerate}
    \item \textbf{The Leptonic Nature ($0\nu\beta\beta$):} Standard physics often invokes Majorana masses ($\mathcal{L}_{M} = -\frac{1}{2}m_L \bar{\nu}_L^c \nu_L$) to explain neutrino lightness. This boundary condition couples a left-handed field to its own charge-conjugated field, requiring the transition to be time-reversal symmetric and forming a standing wave in the temporal dimension. However, the \textbf{Chiral Diode} architecture (Section IV) relies on chiral truncation to break time-reversal symmetry and establish a unidirectional arrow of time. A Majorana mass term represents a bi-directional boundary condition that would allow phase information to propagate backward through the causal loop, causing immediate causal aliasing and phase-lock failure. Consequently, all physical mass terms must be Dirac masses ($m \bar{\nu}_R \nu_L$), which preserve the unidirectional chiral flow. The observation of neutrinoless double-beta decay by upcoming experiments such as LEGEND or nEXO would demonstrate that the Chiral Diode is permeable, falsifying this fundamental causal filter.
    
    \item \textbf{Strict First-Row CKM Unitarity (The Cabibbo Anomaly):} Current experimental fits of the CKM matrix exhibit a $\sim 3\sigma$ deficit in first-row unitarity ($|V_{ud}|^2 + |V_{us}|^2 + |V_{ub}|^2 \approx 0.9985$). In the $E_8$-Persistence framework, the total capacity of the substrate is strictly finite ($\nu=16$) and conserved, forcing the transition matrix to be strictly unitary. This framework predicts that the observed anomaly is entirely an artifact of systematic experimental measurement errors (such as those in superallowed nuclear beta decays). If future high-precision experiments confirm that the first-row sum is genuinely non-unitary (i.e., the anomaly persists or grows as experimental uncertainties shrink), the strict geometric unitarity constraint is falsified.
    
    \item \textbf{The Leptonic CP Phase and Jarlskog Invariant:} Standard global fits treat leptonic CP violation as a free parameters. This framework predicts the leptonic CP phase to be the continuous Golden Angle ($\delta_{CP}^\nu \approx \mathbf{\NuCPVal}$) and the Jarlskog invariant to be the exact projection frustration ($J_{CKM} \approx \mathbf{\JarlskogMatrixVal}$) with zero free parameters. If future high-precision measurements of leptonic CP violation by DUNE, T2K, or Hyper-Kamiokande conclusively exclude these derived values, the framework is falsified.
    
    \item \textbf{Atmospheric Neutrino Mixing and Bulk Running:} The bare atmospheric angle is a maximal-entropy bisection ($\sin^2\theta_{23}^{\text{bare}} = 0.5$) at the unprojected scale. At observable energies, this angle must converge to the dressed value $\sin^2\theta_{23} \approx \mathbf{\AtmosAngleVal}$ under bulk-stiffness scaling (the $\pi/21$ volumetric aperture). If future precision measurements by Hyper-Kamiokande and DUNE place the atmospheric angle in the first octant ($\sin^2\theta_{23} < 0.5$), or if they resolve the value to be significantly different from this calculated bulk running, the volumetric bulk shift hypothesis is falsified.
\end{enumerate}