\section{Discussion}

\subsection{Falsifiable Predictions}

\subsubsection{Impedance Matching (GST)}
The Cabibbo angle is strictly coupled to mass via the relation $\theta_C \approx \sqrt{m_d/m_s}$.

\subsection{Systemic Constraints and No-Go Theorems}

The $E_8$-Persistence Theory enforces strict topological limits on field behavior, providing solutions to long-standing ``fine-tuning" mysteries by identifying them as architectural requirements.

\subsubsection{Prohibition of Neutrinoless Double Beta Decay (\texorpdfstring{$0\nu\beta\beta$}{0nubetabeta})}

Standard physics often invokes \textbf{Majorana masses} and the \textbf{See-saw Mechanism} to explain the extreme lightness of neutrinos relative to the charged leptons. This requires the existence of yet-undiscovered, ultra-heavy right-handed neutrinos.

The $E_8$-Persistence Theory achieves the same mass suppression without additional particles. Neutrino mass scales via \textbf{Inverse Resonance Scaling} ($1/\Delta^n$), where the ``lightness" is a direct function of the lattice's resonant depth. In this framework, the See-saw mechanism is a mathematical artifact; the ``heavy" side of the balance is not a particle, but the \textbf{Heegner Constant ($\Delta$)} itself.

\begin{itemize}
    \item \textbf{The Constraint:} Because the \textbf{Chiral Diode} establishes a strictly directional signal flow, a vibration cannot be its own reflection. Majorana nature is architecturally prohibited.
    \item \textbf{The Decisive Test:} This represents a ``Hard Falsification" point for the model. The observation of neutrinoless double-beta decay by experiments like LEGEND or nEXO would invalidate the Chiral Diode architecture and the $E_8$ substrate logic.
\end{itemize}

\subsubsection{Structural Resonance: The Golden Cost of Time}

We observe a striking geometric relationship between the magnitude of CP Violation ($J$, derived in this paper) and the Vacuum Temporal Tax ($T$, derived in Paper I).

\begin{equation}
\frac{J}{T} = \frac{3.09 \times 10^{-5}}{1.185 \times 10^{-5}} \approx \mathbf{2.61}
\end{equation}

This ratio aligns with the Squared Golden Ratio ($\phi^2 \approx 2.618$) to within 0.4\%.

\textbf{Physical Interpretation:}
\begin{itemize}
    \item $T$ is the entropic cost of a linear time step.
    \item $J$ is the informational asymmetry required to distinguish ``forward" from ``backward."
    \item The relationship $J \approx \phi^2 T$ implies that Time Asymmetry is the icosahedral projection of the entropic cost.
\end{itemize}

\subsection{Scope: Boundary Conditions vs. Dynamics}
This work derives the fundamental constants as the static \textbf{Boundary Conditions} of the vacuum geometry. It does not attempt to derive the dynamic equations of motion (e.g., scattering amplitudes or loop corrections). In this framework, standard Quantum Field Theory is the effective dynamic description of information flowing \textit{through} these fixed geometric apertures. The "running" of constants (Renormalization) is interpreted here as the scale-dependent resolution of the lattice granularity, a topic reserved for future work.